### 2013-09-23 acknowledgements.tex

\section*{ACKNOWLEDGEMENTS}
The authors would like to thank Siemens Medical Solution USA, Ultrasound
Division for their in-kind technical support and Ned Danieley for system administration support.
This work was supported by NIH R01CA142824 and the Duke Coulter Translational Grant Program.

>>>>

\section*{Acknowledgements} 
The authors would like to thank Dr. Ned Rouze for his design of the ultrasound
transducer rotation apparatus and experimental data acquisition, Siemens
Medical Solution USA, Ultrasound Division for their in-kind technical support
and Ned Danieley for computer system administration support.  This work was
supported by NIH R01CA142824 and the Duke Coulter Translational Grant Program.
